---
title: "stat412 final project"
author: "Batuhan SAYLAM"
date: "2024-06-08"
output: pdf_document
---

```{r setup,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,message = FALSE, fig.width=4, fig.height=4)
```



```{r}
library(mice)
library(VIM)
library(corrplot)
library(dplyr)
library(Hmisc)
library("stringr")
library(ggplot2)
library(gridExtra)
library(fastDummies)
library(MASS)
library(factoextra)
library(caret)
library(e1071)
library(pROC)
library(rcompanion)
library(rpart)
library(rpart.plot)
library(xgboost)
library(neuralnet)
library(reshape2)

```



```{r}
data=read.csv("C:/Users/ASUS/Desktop/stat412/Car details v3.csv",na=c(""," "))
```


```{r out.height=4,out.width=4}
head(data)
```


```{r}
summary(data)
```


```{r}
str(data)
```


```{r}
data[duplicated(data),]
```


```{r}
data = data[!duplicated(data),]
data = data[, -which(names(data) == "torque")]
data = data[, -which(names(data) == "seats")]

```




```{r}
str(data)

```


```{r}
colnames(data)[c(3,4,6,11)]=c("sellPrice","kmDriven","sellType","maxPower")
colnames(data)
```


```{r}
data["mileage"]=str_remove(data$mileage," kmpl")
data["mileage"]=str_remove(data$mileage," km/kg")
data["mileage"]=as.numeric(data$mileage)



data["engine"]=str_remove(data$engine," CC")
data["engine"]=as.numeric(data$engine)



data["maxPower"]=str_remove(data$maxPower," bhp")
data["maxPower"]=as.numeric(data$maxPower)
```



```{r}
table(data$fuel)
```




```{r}
table(data$sellType)
```




```{r}
table(data$transmission)

```



```{r}
table(data$owner)
```

```{r}
data$fuel=as.factor(data$fuel)
data$sellType=as.factor(data$sellType)
data$transmission=as.factor(data$transmission)
data$owner=as.factor(data$owner)
data$year=as.factor(data$year)

str(data)
```




```{r}
summary(data)

```






```{r}
numeric_data <- data %>% select_if(is.numeric)
```

```{r}
sapply(numeric_data, sd, na.rm = TRUE)

```

```{r}
plot_list <- list()

# Loop through columns and create boxplots
for (col in colnames(data)) {
  if(is.numeric(data[[col]])){
    plot_list[[col]] <- ggplot(data, aes_string(x = col)) +
        geom_boxplot() +
        labs(title = paste("Boxplot of", col))+theme_classic()}
}

# Plotting
grid.arrange(grobs = plot_list,ncol = 3)
```





```{r}
priceBoxPlot <- boxplot(data$sellPrice,plot = FALSE)
length(priceBoxPlot$out)/length(data$sellPrice)
```




```{r}
outliers <- priceBoxPlot$out
data$sellPrice[data$sellPrice %in% unique(outliers)] <- NA
data$sellPrice[is.na(data$sellPrice)] <- round(mean(data$sellPrice, na.rm = TRUE))
```



```{r}
kmDrivenBoxPlot <- boxplot(data$kmDriven,plot = FALSE)
length(kmDrivenBoxPlot$out)/length(data$kmDriven)
```



```{r}
outliers <- kmDrivenBoxPlot$out
data$kmDriven[data$kmDriven %in% unique(outliers)] <- NA
data$kmDriven[is.na(data$kmDriven)] <- round(mean(data$kmDriven, na.rm = TRUE))
```




```{r}
mileageBoxPlot <- boxplot(data$mileage,plot = FALSE)
length(mileageBoxPlot$out)/length(data$mileage)
```

```{r}
outliers <- mileageBoxPlot$out
data$mileage[data$mileage %in% unique(outliers)] <- NA
data$mileage[is.na(data$mileage)] <- round(mean(data$mileage, na.rm = TRUE))
```


```{r}
engineBoxPlot <- boxplot(data$engine,plot = FALSE)
length(engineBoxPlot$out)/length(data$engine)
```



```{r}
maxPowerBoxPlot <- boxplot(data$maxPower,plot = FALSE)
length(maxPowerBoxPlot$out)/length(data$maxPower)
```




```{r}
outliers <- maxPowerBoxPlot$out
data$maxPower[data$maxPower %in% unique(outliers)] <- NA
data$maxPower[is.na(data$maxPower)] <- round(mean(data$maxPower, na.rm = TRUE))
```






```{r}
numeric_data <- data %>% select_if(is.numeric)
```


**EXPLORATORY DATA ANALYSIS**\

**RQ1) Is the distributions of the numeric variables?**
\


```{r}
par(mfrow=c(3,2))
for(i in 1:min(ncol(numeric_data))){
  hist(numeric_data[,i], main=paste("Histogram of",colnames(numeric_data)[i]), xlab="Values") 
  
}
```




**RQ2) Is the  mileage distrubited normally?**
\

```{r}
par(bg = "#F8F8FF")
hist(data$mileage,main="Histogram of the mileage",xlab="Mileage",col="#00ffff",prob=TRUE,breaks="Scott")
lines(density(data$mileage,na.rm=TRUE),col="red",type="l",lwd=3)

```


```{r}
qqnorm(data$mileage, main = "Q-Q Plot of Mileage")  # Create the Q-Q plot
qqline(data$mileage, col = 2)  
```

**RQ3) In different sales types, does  tranmission type have an impact on sales prices? ?**\

```{r}
ggplot(data=data, aes(x=transmission, y=sellPrice, fill = sellType)) +
  geom_bar(stat="identity", position=position_dodge()) +
  labs(x = "transmission", y = "Sell Price") +
  theme_classic()
```


**RQ4) Is there a statistically significant correlation among numeric  variables?** \


```{r}
corrplot(cor(numeric_data, use = "complete.obs"), method = "number", type = "upper", tl.col = "black", tl.srt = 45) 
```


**RQ5) How is transmission type distributed  according to sell type?**\
```{r}
spineplot(data$transmission,data$sellType ,col = c("aquamarine1","tan1","aquamarine4","chartreuse","deepskyblue","magenta"),xlab="transmission", ylab="sell type",main="Spine-plot for transmission  and sell type")
```

**RQ6) Does the engine affect max power in transmission type?**\



```{r}
ggplot(data=data, aes(x=engine, y=maxPower)) +
  geom_point(aes(color = transmission), alpha = 0.7) +
  labs(x = "Engine", y = "Max Power") +
  facet_wrap(~ transmission, scales = "free") +
  scale_color_manual(values = c("pink","purple"))+
  theme_classic()
```


```{r}
sum(is.na(data))
```

```{r}
md.pairs(data)$mm
```



```{r}
colSums(is.na(data))/nrow(data)

```

```{r}
mice_plot = aggr(data, col=c('darkred','orange'),
                    numbers=TRUE, sortVars=TRUE, prop=FALSE,
                    labels=names(data), cex.axis=.7,
                    gap=3, ylab=c("Missing data","Pattern"))
```


```{r}
dataImp = mice(data,m=5, method = "pmm",seed=1)
```

```{r}
dataComp=complete(dataImp)
```


```{r}
colSums(is.na(dataComp))

```

```{r}
summary(dataComp)
```


```{r}
str(dataComp)
```




```{r}
par(mfrow=c(round(length(numeric_data)/2),2))
for(i in 1:min(ncol(data))){
  if(is.numeric(data[,i])){
    d1=density(na.omit(data[,i])) 
    plot(d1, main=paste("Density of",colnames(data)[i]),xlab="Values",col="blue")
    d2=density(dataComp[,i])
    plot(d2, main=paste("Density of imputed",colnames(dataComp)[i]), xlab="Values",col="red")
    }
}
```

```{r}
trf=boxcox(lm(dataComp$sellPrice~1))

```


```{r}
lambda = trf$x[which.max(trf$y)] #Determine the exact lambda
dataComp["sellPrice"] = (dataComp$sellPrice ^ lambda - 1) / lambda
```



```{r}
trf=boxcox(lm(dataComp$kmDriven~1))

```

```{r}
lambda = trf$x[which.max(trf$y)] #Determine the exact lambda
dataComp["kmDriven"] = (dataComp$kmDriven ^ lambda - 1) / lambda
```

```{r}
trf=boxcox(lm(dataComp$mileage~1))

```

```{r}
lambda = trf$x[which.max(trf$y)] #Determine the exact lambda
dataComp["mileage"] = (dataComp$mileage ^ lambda - 1) / lambda
```



```{r}
trf=boxcox(lm(dataComp$engine~1))

```

```{r}
lambda = trf$x[which.max(trf$y)] #Determine the exact lambda
dataComp["engine"] = (dataComp$engine ^ lambda - 1) / lambda
```


```{r}
trf=boxcox(lm(dataComp$maxPower~1))

```

```{r}
lambda = trf$x[which.max(trf$y)] #Determine the exact lambda
dataComp["maxPower"] = (dataComp$maxPower ^ lambda - 1) / lambda
```




```{r}
numeric_data <- dataComp %>% select_if(is.numeric)
```

```{r}
sapply(numeric_data, sd)

```



```{r}
dim(numeric_data)
```

```{r}
pca = prcomp(numeric_data, scale = TRUE)
summary(pca)
```
```{r}
pca$sdev
```


```{r}
pca$rotation
```


```{r}
biplot(pca, scale = 0,cex=c(0.3,0.7))
```




```{r}
fviz_eig(pca,ncp = 14)
```

Let’s select 2 components:

```{r}
selected_pca=pca$x[,1:2]
head(selected_pca)
```

```{r}
dim(selected_pca)
```
```{r}
cor_check = cor(selected_pca, method="pearson")
cor_check
```


```{r}
dataComp[colnames(selected_pca)]=selected_pca
```


```{r}
dataComp=dummy_cols(dataComp, select_columns = c("fuel","sellType","transmission","owner"), remove_selected_columns = FALSE)

```


**CDA:**\



**RQ1) Is the distributions of the numeric variables?**
\

**RQ2) Is the  mileage distrubited normally?**

Since length of the data is greater than 5000, we cannot aplt shapiro wilk test; hence, we will apply Kolmogorov-Smirnov test.\

Null Hypothesis (H0): \
Sample data comes from the specified distribution\
Alternative Hypothesis (H1):\
Sample data does not come from the specified distribution\


```{r}
ksTestResult <- ks.test(dataComp$mileage, "pnorm", mean(dataComp$mileage), sd(dataComp$mileage))

print(ksTestResult)

```
Since p value is less than 0.05, reject null hypothesis.\



**RQ3) Does the transmission type affect the sell Price in different sell type ?**\


```{r}
ksTestResult <- ks.test(dataComp$sellPrice, "pnorm", mean(dataComp$sellPrice), sd(dataComp$sellPrice))

print(ksTestResult)
```
Since normality assumption is not provided, I used Scheirer-Ray-Hare Test which is the non parametric verison of the two way anova.
```{r}
scheirer_test <- scheirerRayHare(sellPrice ~ transmission + sellType + transmission:sellType, data = dataComp)
print(scheirer_test)

```
Hypothesis 1 (Sell Price DO NOT differ depending on transmission type): 0 < .05

Hypothesis 2 (Sell price levels DO NOT differ depending on sell type): 0 < .05

Hypothesis 3 (The combination of transmission type and sell type is NOT impacting the sell price): 4.4723e-08 < .05

Hypothesis 1: Reject!

Hypothesis 2: Reject!

Hypothesis 3: Reject!


**RQ4) Is there a statistically significant correlation among numeric  variables?** \


```{r}
for(i in 1:(length(colnames(numeric_data))-1)){
  j=i+1
  for(k in j:length(colnames(numeric_data))){
    cat("Correlation Trest for",colnames(numeric_data)[i],"and",colnames(numeric_data)[k],":")
    cor_test_result <- cor.test(numeric_data[,i], numeric_data[,k])
    print(cor_test_result)
  }
}


```




**RQ5) How is transmission type distributed  according to fuel type?**\


```{r}
contingencyTable <- table(dataComp$transmission, dataComp$sellType)
chiSquaredTestResult <- chisq.test(contingencyTable)
print(chiSquaredTestResult)

```



**RQ6) Does the engine affect max power in different fuel type?**\

```{r}
dataAutomatic=dataComp[which(dataComp$transmission=="Automatic"),]
dataManual=dataComp[which(dataComp$transmission=="Manual"),]

```


```{r}

ksTestResult <- ks.test(dataAutomatic$maxPower, "pnorm", mean(dataAutomatic$maxPower), sd(dataAutomatic$maxPower))

print(ksTestResult)

ksTestResult <- ks.test(dataAutomatic$engine, "pnorm", mean(dataAutomatic$engine), sd(dataAutomatic$engine))

print(ksTestResult)
```

```{r}
ksTestResult <- ks.test(dataManual$maxPower, "pnorm", mean(dataManual$maxPower), sd(dataManual$maxPower))

print(ksTestResult)

ksTestResult <- ks.test(dataManual$engine, "pnorm", mean(dataManual$engine), sd(dataManual$engine))

print(ksTestResult)
```








Since both variables are not normally distributed, I will use Spearman correlation test which is alternative of pearson corr. test for nonnormal variables





```{r}
# Spearman Correlation
# Calculate Spearman Correlation for each group
correlation_by_group <- dataComp %>%
  group_by(transmission) %>%
  summarise(correlation = cor(engine,maxPower, method = "spearman"),p_value = cor.test(engine, maxPower, method = "spearman")$p.value)
print(correlation_by_group)

```
Since p values are smaller than 0.05 so there is no corr btw variables according to fuel type.




Model 

```{r}
modelData= dataComp[, -which(names(dataComp) == colnames(data)[0:12])]
modelData= modelData[, -which(names(modelData) == colnames(modelData)[11])]

```


```{r}
set.seed(1)
ind = createDataPartition(modelData$transmission_Automatic, p = 0.8, list = FALSE)
train  = modelData[ind, ] 
test = modelData[-ind, ]
```

```{r}
d_original=dim(modelData)
d_train=dim(train)
d_test=dim(test)
dimens=cbind(d_original,d_train,d_test)
rownames(dimens)=c("number of rows","number of columns")
dimens
```



```{r}
prop.table(table(train$transmission_Automatic))

```

```{r}
table(train$transmission_Automatic)

```

```{r}
prop.table(table(test$transmission_Automatic))

```

```{r}
table(test$transmission_Automatic)

```
```{r}
ggplot(modelData) +
  geom_point(aes(PC1, factor(transmission_Automatic)), color = "blue") +
  labs(x = 'PCA1', y = 'Automatic Transmission')+
  theme_classic()
```

```{r}
ggplot(modelData) +
  geom_point(aes(PC2, factor(transmission_Automatic)), color = "blue") +
  labs(x = 'PCA2', y = 'Automatic Transmission')+
  theme_classic()
```


```{r}
ggplot(modelData, aes(x = factor(transmission_Automatic), y = PC1, fill = factor(transmission_Automatic))) + 
  geom_boxplot() + 
  xlab("transmission_Automatic (Y/N)") + 
  ylab("PC1") + 
  ggtitle("transmission_Automatic and PC1")+
  theme_classic()
```

```{r}
ggplot(modelData, aes(x = factor(transmission_Automatic), y = PC2, fill = factor(transmission_Automatic))) + 
  geom_boxplot() + 
  xlab("transmission_Automatic (Y/N)") + 
  ylab("PC2") + 
  ggtitle("transmission_Automatic and PC2")+
  theme_classic()
```


```{r}
logModel = glm(transmission_Automatic~.,
                 family = binomial,
                 data = train)

summary(logModel)
```

Since p values of fuel_CNG, fuel_LPG, sellType_Dealer, `owner_First Owner` , `owner_Fourth & Above Owner`, `owner_Test Drive Car`, `owner_Second Owner`  are greater than 0.05 and  p values of fuel_Petrol,`sellType_Trustmark Dealer`, `sellType_Trustmark Dealer`,`owner_Third Owner`  are NA, these columns do not affect the model hence we need to remove them. 


```{r}
logmodelTrain= train[, -which(names(train) %in% c("fuel_CNG", "fuel_LPG", "sellType_Dealer", "owner_First Owner" , "owner_Fourth & Above Owner", "owner_Test Drive Car", "owner_Second Owner","fuel_Petrol","sellType_Trustmark Dealer", "sellType_Trustmark Dealer","owner_Third Owner") )]
```


```{r}
logModel = glm(transmission_Automatic~.,
                 family = binomial,
                 data = logmodelTrain)

summary(logModel)
```

Since p values of all variables  are smaller than 0.05, these columns  affect the model. 

```{r}
prop= round(length(subset(train,transmission_Automatic == 1)$transmission_Automatic)/length(train$transmission_Automatic),2)
prop
```



```{r}
glm_pred = ifelse(predict(logModel, test, type = "response") > prop, 1, 0)

```

```{r}
glm_train = ifelse(predict(logModel, train, type = "response") > prop, 1, 0)
```



```{r}
calc_class_err = function(actual, predicted) {
  mean(actual != predicted)
}

calc_class_err(actual = test$transmission_Automatic, predicted = glm_pred)
```


```{r}
testTab= table(predicted = glm_pred,actual = test$transmission_Automatic)
testTab
```
```{r}
testTab3= table(predicted = glm_train,actual = train$transmission_Automatic)
testTab3

```


```{r}
testTab= table(predicted = glm_pred,actual = test$transmission_Automatic)
accuracy=(testTab[1, 1] + testTab[2, 2]) / sum(testTab)
glm_pred=as.factor(glm_pred)
sensitivity=sensitivity(as.factor(test$transmission_Automatic), glm_pred)
specificity=specificity(as.factor(test$transmission_Automatic),glm_pred)
df1=data.frame(accuracy,sensitivity,specificity)
df1
```

```{r}

accuracy=(testTab3[1, 1] + testTab3[2, 2]) / sum(testTab3)
glm_train=as.factor(glm_train)
sensitivity=sensitivity(as.factor(train$transmission_Automatic), glm_train)
specificity=specificity(as.factor(train$transmission_Automatic),glm_train)
df3=data.frame(accuracy,sensitivity,specificity)
df3
```

```{r}
test_prob=predict(logModel, type = "response",newdata = test)
test_roc = roc(test$transmission_Automatic ~ test_prob, plot = TRUE, print.auc = TRUE)
```








tuned_parameter=tune.svm(train[,-10],as.factor(train[,10]),type="C-classification",kernel="linear",gamma = 10^(-5:-1), cost = 10^(-3:1),epsilon = c(0.01,0.05,0.1,0.5,0),scale=FALSE)
tuned_parameter$best.parameters



```{r}
gamma=0.00001
cost=1
epsilon=0.01
```
```{r}
svm_tuned<-svm(transmission_Automatic~.,data=train,kernel="linear",cost=cost,gamma=gamma,epsilon=epsilon,type="C-classification")
svm_tuned
```
```{r}

summary(svm_tuned)
```




```{r}
svm_pred = predict(svm_tuned, test, type = "response")

```

```{r}
svm_train = predict(svm_tuned, train, type = "response")
```

```{r}
calc_class_err = function(actual, predicted) {
  mean(actual != predicted)
}

calc_class_err(actual = as.factor(test$transmission_Automatic), predicted = svm_pred)
```
```{r}
testTab2= table(predicted = svm_pred,actual = as.factor(test$transmission_Automatic))
testTab2
```

```{r}

accuracy=(testTab2[1, 1] + testTab2[2, 2]) / sum(testTab2)
svm_pred=as.factor(svm_pred)
sensitivity=sensitivity(as.factor(test$transmission_Automatic), svm_pred)
specificity=specificity(as.factor(test$transmission_Automatic),svm_pred)
df2=data.frame(accuracy,sensitivity,specificity)
df2
```


```{r}
testTab4= table(predicted = svm_train,actual = as.factor(train$transmission_Automatic))
testTab4
```

```{r}

accuracy=(testTab4[1, 1] + testTab4[2, 2]) / sum(testTab4)
svm_train=as.factor(svm_train)
sensitivity=sensitivity(as.factor(train$transmission_Automatic), svm_train)
specificity=specificity(as.factor(train$transmission_Automatic),svm_train)
df4=data.frame(accuracy,sensitivity,specificity)
df4
```
```{r}
test_prob=predict(svm_tuned, type = "response",newdata = test)
test_roc = roc(test$transmission_Automatic ~ as.numeric(test_prob), plot = TRUE, print.auc = TRUE)
```








```{r}
NBclassfier=naiveBayes( transmission_Automatic ~ . , data=train)
summary(NBclassfier)

```


```{r}
NB_pred = predict(NBclassfier, test, type = "class")

```

```{r}
NB_train = predict(NBclassfier, train, type = "class")
```

```{r}
calc_class_err = function(actual, predicted) {
  mean(actual != predicted)
}

calc_class_err(actual = as.factor(test$transmission_Automatic), predicted = NB_pred)
```
```{r}
testTab2= table(predicted = NB_pred,actual = as.factor(test$transmission_Automatic))
testTab2
```

```{r}

accuracy=(testTab2[1, 1] + testTab2[2, 2]) / sum(testTab2)
NB_pred=as.factor(NB_pred)
sensitivity=sensitivity(as.factor(test$transmission_Automatic), NB_pred)
specificity=specificity(as.factor(test$transmission_Automatic),NB_pred)
df5=data.frame(accuracy,sensitivity,specificity)
df5
```

```{r}
testTab4= table(predicted = NB_train,actual = as.factor(train$transmission_Automatic))
testTab4
```
```{r}

accuracy=(testTab4[1, 1] + testTab4[2, 2]) / sum(testTab4)
svm_train=as.factor(NB_train)
sensitivity=sensitivity(as.factor(train$transmission_Automatic), NB_train)
specificity=specificity(as.factor(train$transmission_Automatic),NB_train)
df6=data.frame(accuracy,sensitivity,specificity)
df6
```
```{r}
test_prob=predict(NBclassfier, type = "class",newdata = test)
test_roc = roc(test$transmission_Automatic ~ as.numeric(test_prob), plot = TRUE, print.auc = TRUE)
```





```{r}
fitDT <- rpart(transmission_Automatic~., data = train, method = 'class')

```

```{r}
rpart.plot(fitDT)

```





```{r}
train_pred <-predict(fitDT,train[,-10],type = 'class')
calc_class_err(train_pred,train[,10])
```


```{r}
test_pred <-predict(fitDT,test[,-10],type = 'class')
calc_class_err(test_pred,test[,10])
```
```{r}
testTab2= table(predicted = test_pred,actual = as.factor(test$transmission_Automatic))
testTab2
```


```{r}

accuracy=(testTab2[1, 1] + testTab2[2, 2]) / sum(testTab2)
test_pred=as.factor(test_pred)
sensitivity=sensitivity(as.factor(test$transmission_Automatic), test_pred)
specificity=specificity(as.factor(test$transmission_Automatic),test_pred)
df7=data.frame(accuracy,sensitivity,specificity)
df7
```
```{r}
testTab4= table(predicted = train_pred,actual = as.factor(train$transmission_Automatic))
testTab4
```

```{r}

accuracy=(testTab4[1, 1] + testTab4[2, 2]) / sum(testTab4)
train_pred=as.factor(train_pred)
sensitivity=sensitivity(as.factor(train$transmission_Automatic), train_pred)
specificity=specificity(as.factor(train$transmission_Automatic),train_pred)
df8=data.frame(accuracy,sensitivity,specificity)
df8
```
```{r}
test_prob=predict(fitDT, type = "class",newdata = test)
test_roc = roc(test$transmission_Automatic ~ as.numeric(test_prob), plot = TRUE, print.auc = TRUE)
```





```{r}
xgboost_model <- xgboost(data = as.matrix(train[, -10]), 
                         label = train[,10],
                         max_depth = 3, 
                         objective = "binary:logistic", 
                         nrounds = 10, 
                         verbose = FALSE)
summary(xgboost_model)
```


```{r}
train_pred <-ifelse(predict(xgboost_model,as.matrix(train[,-10]),type = 'response')>prop,1,0)
calc_class_err(train_pred,train[,10])
```


```{r}
test_pred <-ifelse(predict(xgboost_model,as.matrix(test[,-10]),type = 'response')>prop,1,0)
calc_class_err(test_pred,test[,10])
```

```{r}
testTab2= table(predicted = test_pred,actual = as.factor(test$transmission_Automatic))
testTab2
```


```{r}
accuracy=(testTab2[1, 1] + testTab2[2, 2]) / sum(testTab2)
test_pred=as.factor(test_pred)
sensitivity=sensitivity(as.factor(test$transmission_Automatic), test_pred)
specificity=specificity(as.factor(test$transmission_Automatic),test_pred)
df9=data.frame(accuracy,sensitivity,specificity)
df9
```


```{r}
testTab4= table(predicted = train_pred,actual = as.factor(train$transmission_Automatic))
testTab4
```


```{r}
accuracy=(testTab4[1, 1] + testTab4[2, 2]) / sum(testTab4)
train_pred=as.factor(train_pred)
sensitivity=sensitivity(as.factor(train$transmission_Automatic), train_pred)
specificity=specificity(as.factor(train$transmission_Automatic),train_pred)
df10=data.frame(accuracy,sensitivity,specificity)
df10
```
```{r}
test_prob=ifelse(predict(xgboost_model, type = "class",newdata = as.matrix(test$transmission_Automatic))>prop,1,0)
test_roc = roc(test$transmission_Automatic ~ as.numeric(test_prob), plot = TRUE, print.auc = TRUE)
```






```{r}
colnames(train)=make.names(colnames(train))
colnames(test)=make.names(colnames(test))
```




```{r}
nn_one=neuralnet(transmission_Automatic~.,data=train,linear.output = FALSE,act.fct = "logistic")
summary(nn_one)
```

```{r}
train_pred <-ifelse(predict(nn_one,train,type = 'response')>prop,1,0)
calc_class_err(train_pred,train[,10])
```


```{r}
test_pred <-ifelse(predict(nn_one,test,type = 'response')>prop,1,0)
calc_class_err(test_pred,test[,10])
```


```{r}
testTab2= table(predicted = test_pred,actual = as.factor(test$transmission_Automatic))
testTab2
```


```{r}

accuracy=(testTab2[1, 1] + testTab2[2, 2]) / sum(testTab2)
test_pred=as.factor(test_pred)
sensitivity=sensitivity(as.factor(test$transmission_Automatic), test_pred)
specificity=specificity(as.factor(test$transmission_Automatic),test_pred)
df11=data.frame(accuracy,sensitivity,specificity)
df11
```


```{r}
testTab4= table(predicted = train_pred,actual = as.factor(train$transmission_Automatic))
testTab4
```

```{r}

accuracy=(testTab4[1, 1] + testTab4[2, 2]) / sum(testTab4)
train_pred=as.factor(train_pred)
sensitivity=sensitivity(as.factor(train$transmission_Automatic), train_pred)
specificity=specificity(as.factor(train$transmission_Automatic),train_pred)
df12=data.frame(accuracy,sensitivity,specificity)
df12
```
```{r}
test_prob=ifelse(predict(nn_one, type = "response",newdata = test)>prop,1,0)
test_roc = roc(test$transmission_Automatic ~ as.numeric(test_prob), plot = TRUE, print.auc = TRUE)
```




```{r}
merged_df <- rbind(df1, df2)
merged_df = rbind(merged_df,df3)
merged_df=rbind(merged_df,df4)
merged_df = rbind(merged_df,df5)
merged_df=rbind(merged_df,df6)
merged_df = rbind(merged_df,df7)
merged_df=rbind(merged_df,df8)
merged_df = rbind(merged_df,df9)
merged_df=rbind(merged_df,df10)
merged_df = rbind(merged_df,df11)
merged_df=rbind(merged_df,df12)
rownames(merged_df)=c("LogModel Test","SVM Test","LogModel Train","SVM Train","NBClassifier Test","NBClassifier Train","DecisionTree Test","DecisionTree Train","XGBoost Test","XGBoost Train","NN_One Test","NN_One Train")
merged_df

```